Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-24 Paper/Paper.tex
number added for bar length

We use the bar segmentation obtained from the Echo Nest analysis to
break a song into a collection of beat-chroma ``patches'', typically
one or two bars in length.
%
Because the bar length varies, depending on the meter of a particular
song, we resample each patch to a fixed length of typically 4 beats
per bar.  Since the overwhelming majority (85\%) of our training data
consisted of bars that were 4 beats long, this resampling was not
often required.  Most of the remaining bars (14\%) were 3 beats in
length.  (FIXME: thierry, can you check these numbers, I'm making them
up based on the deletedfigure)
% although the majority of the data contains bars that are 4 beats long
The resulting patches consist of $12 \times 4$ or $12 \times 8$ matrices.

>>>>

We use the bar segmentation obtained from the Echo Nest analysis to
break a song into a collection of beat-chroma ``patches'', typically
one or two bars in length.
%
Because the bar length varies, depending on the meter of a particular
song, we resample each patch to a fixed length of typically 4 beats
per bar.  Since the overwhelming majority (82\%) of our training data
consisted of bars that were 4 beats long, this resampling was not
often required.  Most of the remaining bars (10\%) were 3 beats in
length.
% although the majority of the data contains bars that are 4 beats long
The resulting patches consist of $12 \times 4$ or $12 \times 8$ matrices.
